Two Mode Networks and Relational Similarity

### 2023-09-08 analysis.qmd
Updated simrank plot

    png(file = here("Plots", "eigvec.png"), width=1000, height=600)
        (a | b) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
    dev.off() 
```

@@

```{r SimRank Plot}
   source(here("Functions", "TwoModeSR.R"))
   tmSR.res <- TwoModeSR(A, C = 0.8, iter = 10)
    a <- tmSR.res$eigvec.plot.r + theme(axis.text = element_blank())
    b <- tmSR.res$eigvec.plot.c 
    c <- tmSR.res$eigval.plot.r
    d <- tmSR.res$eigval.plot.c
    #a <- a + inset_element(c, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    #b <- b + inset_element(d, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    e <- tmSR.res$A.plot
    f <- tmSR.res$corr.plot
   dat.r <- data.frame(ca = as.numeric(tmCA.res$ca.eigvec.r[,1]),
                       sr = tmSR.res$ov.r,
                       lab = rownames(A))
   dat.c <- data.frame(ca = as.numeric(tmCA.res$ca.eigvec.c[,1]),
                       sr = tmSR.res$ov.c,
                       lab = colnames(A))
   g <- ggscatter(dat.r, x = "ca", y = "sr", 
                  label = "lab", repel = TRUE, 
                  add = "reg.line", 
                  add.params = list(color = "gray80", linewidth = 0.25))
   h <- ggscatter(dat.c, x = "ca", y = "sr", 
                  label = "lab", repel = TRUE, 
                  add = "reg.line",
                  add.params = list(color = "gray80", linewidth = 0.25))
   i <- (a | b | (g / h)) + plot_layout(widths = c(2, 2, 1))
   j <- (e | f) + plot_layout(widths = c(1, 3))

   png(file = here("Plots", "sr-plot.png"), width=1000, height=1200)
       (i / j ) +
       plot_annotation(tag_levels = "a") &
       theme(plot.tag = element_text(size = 20))
    dev.off()

@@

```{r}
```

```{r}

>>>>

    png(file = here("Plots", "ca-eigvec.png"), width=1000, height=600)
        (a | b) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
    dev.off() 
```

@@

```{r SimRank Plot}
   source(here("Functions", "TwoModeSR.R"))
   tmSR.res <- TwoModeSR(A, C = 0.8, iter = 10)
    a <- tmSR.res$eigvec.plot.r + theme(axis.text = element_blank())
    b <- tmSR.res$eigvec.plot.c 
    c <- tmSR.res$eigval.plot.r
    d <- tmSR.res$eigval.plot.c
    #a <- a + inset_element(c, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    #b <- b + inset_element(d, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    e <- tmSR.res$A.plot
    f <- tmSR.res$corr.plot
   dat.r <- data.frame(ca = as.numeric(tmCA.res$ca.eigvec.r[,1]),
                       sr = tmSR.res$ov.r,
                       lab = rownames(A))
   dat.c <- data.frame(ca = as.numeric(tmCA.res$ca.eigvec.c[,1]),
                       sr = tmSR.res$ov.c,
                       lab = colnames(A))
   g <- ggscatter(dat.r, x = "ca", y = "sr", 
                  label = "lab", repel = TRUE, 
                  add = "reg.line", 
                  add.params = list(color = "gray80", linewidth = 0.5, linetype = 2))
   h <- ggscatter(dat.c, x = "ca", y = "sr", 
                  label = "lab", repel = TRUE, 
                  add = "reg.line",
                  add.params = list(color = "gray80", linewidth = 0.5, linetype = 2))
   i <- (a | b | e) 
   j <- (f | (g / h)) + plot_layout(widths = c(2.5, 1))
   png(file = here("Plots", "sr-plot.png"), width=1200, height=1200)
       (i / j) +
       plot_annotation(tag_levels = "a") &
       theme(plot.tag = element_text(size = 20))
    dev.off()

@@
